Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
updated image reseutls

Similarly to the UCI experiments, we seek to demonstrate \our on image data that features more complicated data manifolds and model structures. We consider the MNIST and Fashion-MNIST (FMNIST) classification tasks, and use a CNN architecture (matching the setup in \cite{immer2021improving}). After training, we computed the duals for \our and use the model for prediction (full experiment details in \cref{app:image}). In \cref{tbl:imagesuper}, we compare to baselines also used in \cite{immer2021improving}. For \our and the GP predictive subset method by \cite{immer2021improving} we fix the number of points $M=1024$. For the baseline we additionally include a higher $M$ for comparison. We report accuracy (ACC), NLPD, and expected calibration error (ECE). The results in \cref{tbl:imagesuper} agree with the conclusions drawn from the UCI experiments showing that \our is able to more efficiently capture the posterior using a sparse set of points. These results on image data motivates, the experiments that follow that consider learning beyond the supervised learning setting. 
%We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert]. We ran the experiment over $5$ seeds. During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.

>>>>

Similarly to the UCI experiments, we seek to demonstrate \our on image data that features more complicated data manifolds and model structures. We consider the MNIST and Fashion-MNIST (FMNIST) classification tasks, and use an MLP and a CNN architecture respectively (matching the setup in \cite{immer2021improving}). After training, we computed the duals for \our and use the model for prediction (full experiment details in \cref{app:image}). In \cref{tbl:imagesuper}, we compare to baselines also used in \cite{immer2021improving}. For \our and the GP predictive subset method by \cite{immer2021improving} we fix the number of points $M=1024$. For completeness, we include the GP predictive result from \cite{immer2021improving} which used more inducing points $M=3200$. We report accuracy (ACC), NLPD, and expected calibration error (ECE). The results in \cref{tbl:imagesuper} agree with the conclusions drawn from the UCI experiments showing that \our is able to more efficiently capture the posterior using a sparse set of points. These results on image data sets motivate experiments beyond the supervised learning setting, which we now detail.
%We performed hyperparameter optimization over the prior precision, and found the optimal value to be [insert]. We ran the experiment over $5$ seeds. During the NN training, we used a batch size of $512$ and an Adam optimizer with learning rate $1e-3$.
